\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}
\raggedright\hfill\break

This project has been made possible by a number of people and it is my pleasure to convey my appreciation to them in this acknowledgement.\newline

I would like to express my gratitude to my academic supervisor, Colin Coates. Without Colin's invaluable expertise, encouragement, patience and support, this project would not have been possible. His guidance throughout the year has allowed me to spend my time effectively, enhancing the focus of the work produced. I could not have completed this without his guidance.\newline

In addition to my supervisor, I would like to thank the other academics and lab staff who have provided much assistance throughout my degree. Specifically Phillip Dombkins, without Phillip much of the research and development of pneumatic muscles would not have been possible.\newline

My thanks also goes to NUbots which has provided me invaluable experience
throughout my degree. The experience gained through the variety of humanoid robotic projects has given me an insight and passion for the field, and provided part of the inspiration to undertake this project.\newline

I would also like to thank my fellow students for the stimulating discussions, brainstorming
sessions, encouragement and company during the numerous sleepless nights working towards
deadlines over the course of this degree.\newline

Last but certainly not least, I would like to thank my family and friends for their love and
support throughout my life, and in particular, this very challenging year.